Selecting similar behaving group of customers to check clustering methodology

### 2021-10-14 supplementary/distance-computation/real-data/04handpick-from356-mds.Rmd
interactive

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
library(plotly)
library(gracsr)
library(here)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
library(plotly)
#remotes::install_github("Sayani07/gracsr")
library(gracsr)
library(here)
```
